Recurrent Deep Learning Models and its applications

### 2025-01-21 paper/main.tex
merge

\newpage
% Actication function
\textbf{Activation function}\\
Activation functions, particularly the sigmoid function, are fundamental components of recurrent neural networks (RNNs). They transform input data into output data. A key property of these functions is their differentiability. Differentiability is crucial for the backpropagation through time (BPTT) algorithm, enabling the application of the chain rule during training. 
\begin{equation}
    Sigmoid(x) = \frac{ 1 }{ 1+e^{-x} }
\end{equation}
\begin{equation}
    Sigmoid'(x) = Sigmoid(x)(1-Sigmoid(x))
\end{equation}
Below is the sigmoid function and its derivative.
\begin{figure}[!htb]
    \centering
    \includegraphics[width=1\textwidth]{./Pic/sigmoid.png} % Replace "example-image" with your image file
    % \caption{An example image.}
    \label{fig:sigmoid}
\end{figure}
\newline
$Domain(Sigmoid(x))=\mathbb{R},\hspace{1em} Codomain(Sigmoid(x))=(0,1)$\\
$Domain(Sigmoid'(x))=\mathbb{R},\hspace{1em} Codomain(Sigmoid'(x))=[0,0.5]$

% Hyperbolic tangent activation function
\newpage
\textbf{Hyperbolic tangent activation function}\\
The main role of the hyperbolic tangent (tanh) activation function is to normalize candidate values and convert the cell state to a hidden state when performing cell state updates. It limits the output between [-1,1] because it has a stable gradient, which is important for discovering long-range dependencies.
\newline
\begin{equation}
    tanh(x) = \frac{ e^{x} - e^{-x} }{e^{x} + e^{-x}}
\end{equation}
\begin{equation}
    tanh'(x) = 1 - tanh^{2}(x)
\end{equation}
Below is the Hyperbolic tangent activation function and its derivative.\\
\begin{figure}[!htb]
    \centering
    \includegraphics[width=1\textwidth]{./Pic/tanh.png} % Replace "example-image" with your image file
    % \caption{An example image.}
    \label{fig:tanh}
\end{figure}
\newline
$Domain(tanh(x))=\mathbb{R},\hspace{1em} Codomain(tanh(x))=[-1,1]$\\
$Domain(tanh'(x))=\mathbb{R},\hspace{1em} Codomain(tanh'(x))=[0,1]$

>>>>

\newpage
% Actication function
\textbf{Activation function}\\
Activation functions, particularly the sigmoid function, are fundamental components of recurrent neural networks (RNNs). They transform input data into output data. A key property of these functions is their differentiability. Differentiability is crucial for the backpropagation through time (BPTT) algorithm, enabling the application of the chain rule during training. 
\begin{equation}
    Sigmoid(x) = \frac{ 1 }{ 1+e^{-x} }
\end{equation}
\begin{equation}
    Sigmoid'(x) = Sigmoid(x)(1-Sigmoid(x))
\end{equation}
Below is the sigmoid function and its derivative.
\begin{figure}[!htb]
    \centering
    \includegraphics[width=1\textwidth]{../Pic/sigmoid.png} % Replace "example-image" with your image file
    % \caption{An example image.}
    \label{fig:sigmoid}
\end{figure}
\newline
$Domain(Sigmoid(x))=\mathbb{R},\hspace{1em} Codomain(Sigmoid(x))=(0,1)$\\
$Domain(Sigmoid'(x))=\mathbb{R},\hspace{1em} Codomain(Sigmoid'(x))=[0,0.5]$

% Hyperbolic tangent activation function
\newpage
\textbf{Hyperbolic tangent activation function}\\
The main role of the hyperbolic tangent (tanh) activation function is to normalize candidate values and convert the cell state to a hidden state when performing cell state updates. It limits the output between [-1,1] because it has a stable gradient, which is important for discovering long-range dependencies.
\newline
\begin{equation}
    tanh(x) = \frac{ e^{x} - e^{-x} }{e^{x} + e^{-x}}
\end{equation}
\begin{equation}
    tanh'(x) = 1 - tanh^{2}(x)
\end{equation}
Below is the Hyperbolic tangent activation function and its derivative.\\
\begin{figure}[!htb]
    \centering
    \includegraphics[width=1\textwidth]{../Pic/tanh.png} % Replace "example-image" with your image file
    % \caption{An example image.}
    \label{fig:tanh}
\end{figure}
\newline
$Domain(tanh(x))=\mathbb{R},\hspace{1em} Codomain(tanh(x))=[-1,1]$\\
$Domain(tanh'(x))=\mathbb{R},\hspace{1em} Codomain(tanh'(x))=[0,1]$
